---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hrbrmstr/mgrs?branch=master&svg=true)](https://ci.appveyor.com/project/hrbrmstr/mgrs)
[![codecov](https://codecov.io/gh/hrbrmstr/mgrs/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/mgrs)
[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/mgrs.svg?branch=master)](https://travis-ci.org/hrbrmstr/mgrs)
[![keybase verified](https://img.shields.io/badge/keybase-verified-brightgreen.svg)](https://gist.github.com/hrbrmstr/be2f2c14fd78cac24697)

# mgrs

Convert 'MGRS' (Military Grid Reference System) References To and From Other Coordinate Systems

## Description

Essentially, a lightweight R wrapper around bits of <https://svn.osgeo.org/gdal/trunk/gdal/frmts/nitf/>.

Decent reference on MGRS & UTM (Universal Transverse Mercator): <https://www.luomus.fi/en/utm-mgrs-atlas-florae-europaeae>.

## What's inside the tin?

The following functions are implemented:

- `latlng_to_mgrs`:	Convert latitude/longitude to MGRS string 
- `mgrs_to_latlng`:	Convert an MGRS string to latitude/longitude **(now returns a `data.frame`)**
- `mgrs_to_ups`:	Convert MGRS to UPS
- `mgrs_to_utm`:	Convert MGRS to UTM
- `ups_to_mgrs`:	Convert UPS to MGRS
- `utm_to_mgrs`:	Convert UTM to MGRS
- `mgrs_precision`: Return MGRS grid reference precision (in meters)

## TODO

- Find all the folks/projects I need to add in the `DESCRIPTION` for auth/ctb & docs
- Vectorize ALL THE THINGS
- <strike>Add in support for the other MGRS conversion thingys</strike>
- More error checking (basic checking is done)
- Precision validation
- More tests (basic testing is done)

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/mgrs")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(mgrs)

# current verison
packageVersion("mgrs")

mgrs_to_latlng("33UXP04")

latlng_to_mgrs(48.20535, 16.34593)

mgrs_to_latlng("33UXP0500444996")

latlng_to_mgrs(48.24948, 16.41449)

mgrs_to_latlng("24XWT783908")

latlng_to_mgrs(83.62738, -32.66879)

utm_to_mgrs(48, "N", 377299, 1483035)

mgrs_to_utm("48PUV7729883034")

ups_to_mgrs("N", 2426773, 1530125)

mgrs_to_ups("ZGC2677330125")

grefs <- c("4Q", "4QFJ", "4QFJ16", "4QFJ1267", "4QFJ123678",
           "4QFJ12346789", "4QFJ1234567890")
mgrs_precision(grefs)
```

### Visual Verification

```{r fig.retina=2, fig.width=10, fig.height=5}
library(purrr)
library(ggplot2)

# precision == 1

c("16SEB20", "09UXQ25", "12SVC48", "15SWU64", "11SKA54", "13SDC58", 
"18TYM20", "18SWH08", "17RML38", "17SKR77", "09RYR61", "12TTP62", 
"16TBK93", "16TEK73", "15TVG64", "14SNH75", "16SFG94", "15RWP68", 
"19TEL05", "18SUJ54", "19TBG89", "16TFN87", "15TUM73", "16SBB31", 
"15SWC44", "12TXS28", "14TML57", "11SND12", "19TCJ00", "18SWK62", 
"13SDU11", "18TVN87", "17SQV22", "14TMT13", "17TLE65", "14SPE73", 
"10TGP36", "18TTL93", "19TCG20", "17SNT42", "14TMQ40", "16SEE44", 
"14RNV27", "12SVJ72", "18TXQ90", "17SQB46", "11TKN95", "17SNC25", 
"16TBQ64", "13TCH16") -> mgrs_state_centers

mgrs_to_latlng(mgrs_state_centers) %>% 
  ggplot(aes(lng, lat)) +
  geom_point(shape=22, size=2, color="white", fill="black") +
  coord_map("polyconic")
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.