---
output: rmarkdown::github_document
---

`mgrs` : Convert 'MGRS' (Military Grid Reference System) References To and From Other Coordinate Systems

Essentially, a lightweight R wrapper around bits of <https://svn.osgeo.org/gdal/trunk/gdal/frmts/nitf/>.

Decent reference on MGRS & UTM (Universal Transverse Mercator): <https://www.luomus.fi/en/utm-mgrs-atlas-florae-europaeae>.

The following functions are implemented:

- `latlng_to_mgrs`:	Convert latitude/longitude to MGRS string
- `mgrs_to_latlng`:	Convert an MGRS string to latitude/longitude
- `mgrs_to_ups`:	Convert MGRS to UPS
- `mgrs_to_utm`:	Convert MGRS to UTM
- `ups_to_mgrs`:	Convert UPS to MGRS
- `utm_to_mgrs`:	Convert UTM to MGRS

### TODO

- Find all the folks/projects I need to add in the `DESCRIPTION` for auth/ctb & docs
- Vectorize ALL THE THINGS
- Add in support for the other MGRS conversion thingys
- Error checking
- Precision validation
- Tests (etc)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/mgrs")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(mgrs)

# current verison
packageVersion("mgrs")

mgrs_to_latlng("33UXP04")

latlng_to_mgrs(48.20535, 16.34593)

mgrs_to_latlng("33UXP0500444996")

latlng_to_mgrs(48.24948, 16.41449)

mgrs_to_latlng("24XWT783908")

latlng_to_mgrs(83.62738, -32.66879)

utm_to_mgrs(48, "N", 377299, 1483035)

mgrs_to_utm("48PUV7729883034")

ups_to_mgrs("N", 2426773, 1530125)

mgrs_to_ups("ZGC2677330125")
```
